Models

### 2023-02-07 Code/Models.Rmd
Included clusrank comparisons

>>>>

##2019 vs 2022 Comparisons
```{r}
comp <- read.csv("../Data/2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Athlete", "Country", "NineteenH", "NineteenS", "NineteenF", "TwentyTwoH", "TwentyTwoS", "TwentyTwoF")
#View(comp)
```

```{r}
library(clusrank)
t.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
clusWilcox.test(comp$NineteenH, cluster=comp$TwentyTwoH, paired = TRUE, alternative = "greater")
wilcox.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
```

```{r}
t.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
clusWilcox.test(comp$NineteenS, cluster=comp$TwentyTwoS, paired = TRUE, alternative = "greater")
wilcox.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
```

```{}
A matched pairs t test, clusrank package Wilcox test, and a standard Wilcox test all showed that the heat means differ by a significant amount. And two of the three semifinals means had an alpha less than 0.01.
```

```{r}
nations <- read.csv("../Data/NatVSWorld.csv")
colnames(nations) <- c("Athlete", "Country", "NatH", "NatS", "NatF", "WorldH", "WorldS", "WorldF")
```

```{r}
library(clusrank)
t.test(nations$NatH, nations$WorldH, paired = TRUE)
clusWilcox.test(nations$NatH, cluster=nations$WorldH, paired = TRUE, alternative = "greater")
wilcox.test(nations$NatH, nations$WorldH, paired = TRUE)
```
```{}
These p values all significant at alpha = 0.05, but not at alpha = 0.01
```

```{r}
library(clusrank)
t.test(nations$NatS, nations$WorldS, paired = TRUE)
clusWilcox.test(nations$NatS, cluster=nations$WorldS, paired = TRUE, alternative = "greater")
wilcox.test(nations$NatS, nations$WorldS, paired = TRUE)
```
```{}
These p values are all significant at alpha = 0.01
```
